Ring of Fire Camera Detections Report

### 2023-02-22 analysis/paper/paper.qmd
update

Images were retrieved from all cameras using a SD card reader and copied onto a 10 TB harddrive od brand LaCie. The images amounted to 1.8TB of memory on disk, for a total of 2,788,375 images. Images were stored with the following directory structure:

@@

About 46.22 % of the images, or 1,289,022 images, were found by the model to possibly have either a person, animal, or vehicle. The model did not produce detections for 1,499,353 images, or 53.77 % of the total.
This resulted in a total of 2,889,195 detections. The totals for each category are: 1,691,444 animals (or 58.54 %); 989,112 persons (or 34.23 %); and 208,639 vehicles (or 7.22 %).

@@

Out of the 189,982 animal detections, 65,338 have been processed on the platform (34.39 %) for a total of 54,677 images (1.96 % of the total amount of images, or 4.24 % of the set of images with at least one detection, or 19.44 % of the total amount of images uploaded to the platform). This does not include the empty images also viewed as part of a set, bringing that amount to 92,826 “detections” and 82,165 images, (2.94 % of the total amount of images, or 29.21 % of the total amount of images uploaded to the platform).
Out of the 65,338 detections, 30,621 were false positives (46,87 %), and 33,237 were true positives (50.86 %), to which 1,480 false negatives were added (manually added bounding boxes, 2.26 %).

>>>>

Images were retrieved from all cameras using a SD card reader and copied onto a 10 TB hard drive of brand LaCie. The images amounted to 1.8TB of memory on disk, for a total of __`r length(unique(dets$image_id))`__ images. Images were stored with the following directory structure:

@@

About 46.22 % of the images, or 1,289,022 images, were found by the model to possibly have either a person, animal, or vehicle. The model did not produce detections for 1,499,353 images, or 53.77 % of the total.

This resulted in a total of 2,889,195 detections. The totals for each category are: 1,691,444 animals (or 58.54 %); 989,112 persons (or 34.23 %); and 208,639 vehicles (or 7.22 %).

@@

Out of the 189,982 animal detections, 65,338 have been processed on the platform (34.39 %) for a total of 54,677 images (1.96 % of the total amount of images, or 4.24 % of the set of images with at least one detection, or 19.44 % of the total amount of images uploaded to the platform). This does not include the empty images also viewed as part of a set, bringing that amount to 92,826 “detections” and 82,165 images, (2.94 % of the total amount of images, or 29.21 % of the total amount of images uploaded to the platform).

Out of the 65,338 detections, 30,621 were false positives (46,87 %), and 33,237 were true positives (50.86 %), to which 1,480 false negatives were added (manually added bounding boxes, 2.26 %).
